HW #4: Analyze real-world emissions data

### 2022-12-03 HW4/HW4.Rmd
do hw4.3

# 3

>>>>

# 3 (3.1)

The theory behind I/M programs is good, in that vehicles with high emissions are kept from operation. However, as mentioned, this creates issues with equity, where these programs impact lower income individuals more than higher income individuals. Perhaps one of the main reasons for this is due to the age of the vehicles owned based on income. Newer vehicles are more fuel efficient as well as lower-emitting than older vehicles (at least as a rule), especially as emissions standards continue to get stricter. Newer vehicles are also significantly more expensive than older vehicles, and so are less likely to be owned by lower income individuals.

But this does not wholly discount the benefit of I/M programs. In fact, I'd argue these programs (or at least the concept of them) are a good thing so long as equity can be addressed properly. Perhaps funds that would have gone to I/M programs could be used as a subsidy for low-income individuals to purchase more climate-friendly vehicles. Though this doesn't address the question of what to do with high-emitting vehicles directly, increasing the gas/diesel tax would discourage driving as much (lowering emissions), and then the excess funds could again be used as subsidies for low- to no-emitting vehicles.
